Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-26 response/response.tex

{%\color{blue}
We thank the Guest Editors for the efforts of handling our submission and two reviewers for providing the constructive and valuable feedback.
The detailed comments help us further improve the quality of our manuscript.
%The changes made to the manuscript are highlighted in blue text.
In the following, we list our detailed responses to all the comments.
For your convenience, we add a separate reference list in the end that is used in this response letter.
}

\vspace{2em}
\noindent {\large\textsc{Reviewer~1}}\\
\begin{tabular*}{\textwidth}{c}
\hline
\end{tabular*}

% Reviewer 1: Q1
\begin{review}
The text (including the abstract) contains many typographical and grammatical errors, which are distracting and render the manuscript difficult to read.
The authors should proofread the document carefully.
\end{review}

\begin{response}
We have proofread it very carefully and corrected some typos and grammar errors. 
\end{response}

@@

\begin{response}
We have added two paragraphs with related references to better connect plant phenotyping and computer vision tasks.
Please refer to paragraph $2$ and $3$ in Sec. $1$.
\end{response}

% Reviewer 1: Q3
\begin{review}
The authors should clarify what is intended by ``leaf alignment" and why it is important, since this feature is probably less common in plant phenotyping applications than the others that are mentioned.
\end{review}

\begin{response}
Leaf alignment aims to estimate the structure of a leaf.
In the case where the leaf structure is simple (e.g., ellipsoid-shaped leaf), leaf alignment amounts to estimating the inner and outer tips of the leaf.
For more complex leaf structure (e.g., maple leaf), leaf alignment will estimate additional landmarks on the leaf contour that will consistently appear in all leaves.
Leaf alignment is important for two reasons:
First, it goes beyond leaf segmentation and provides structural information of a leaf - a discriminative signature for a leaf.
For example, ~\cite{cerutti2013understanding} uses a polygonal leaf model for leaf segmentation and plant identification.
Second, plant biologists often hypothesize that different local parts of a leaf may have different photosynthetic efficiency.
This leaf structure information can be used to quantitatively study this hypothesis and its implication to the overall photosynthetic efficiency of a plant.
\end{response}

% Reviewer 1: Q4
\begin{review}
Since multi-modality is a strength of the proposed dataset, the authors should motivate better their choice of imaging modalities (i.e. fluorescence, infrared, RGB color, and depth), highlight their importance and what information they convey on plant structure and functions.
Apparently, this is only partly done for depth at the end of Sec. $2$.
\end{review}

@@

\begin{response}
We have inserted a brief explanation with references in the last paragraph of Sec. $2$.
\end{response}

% Reviewer 1: Q5
\begin{review}
Figure $1$ should be augmented (or a separate figure should be created) with zoom in details showing how the same plant parts (or scene portions) appear in different modalities.
This would help the reader get a better idea of the contrast and the type of information conveyed by each of the modalities adopted by the authors.
\end{review}

\begin{response}
We have augmented Figure $1$ by adding one zoom-in view for one Arabidopsis plant.
Since bean dataset only contains one plant with good view, we do not provide a zoom-in view.
\end{response}

@@

% Reviewer 1: Q6
\begin{review}
Each of the databases mentioned in Table $1$ should be accompanied by a reference.
\end{review}

\begin{response}
We have the corresponding references in Sec. $2$, which follows the order as they appear in Table $2$.
To make it complete, we also added the references to Table $2$.
\end{response}

@@

% Reviewer 1: Q8
\begin{review}
In the second paragraph in Sec. $2$, I believe the observation on single leaves imaged in a constrained environment does not apply to the dataset by (Haug and Ostermann, $2014$).
Please reformulate.
\end{review}

\begin{response}
It is correct that the dataset (Haug and Ostermann, $2014$) is not about single leaves imaged in a constrained environment.
We still category it in the first type because it does not include leaf segmentation.
All segmentation tasks are based on plant level.
We have reformulated this in the second paragraph in Sec. $2$.
\end{response}

% Reviewer 1: Q9
\begin{review}
It appears from Sec. $3.1$ that all plant subjects (respectively for Arabidopsis and bean) belong to the same genotype and that no treatments were performed.
This would entail that the proposed dataset cannot be used to investigate computer vision algorithms or imaging modalities in relation to group differences.
Could the authors comment on this?
\end{review}

\begin{response}
It is true that we do not compare group differences, based on morphology (for example).
However, we are using this database to address a fundamental issue with visual phenotyping: accurate and automated identification and tracking of individual leaves over developmental time scales (weeks).
The reason this is important is highlighted in other sections, in particular in text we are adding to address Comment $2$ and $4$.
The inherent challenge is that leaves change in size, position, and shape as they emerge and grow.
Also they may overlap or be overlapped by other leaves.
We emphasize more on leaf identification and tracking rather than developing methods/algorithms to define group differences.
We have added one paragraph in Conclusion to better reflect this.
\end{response}

@@

% Reviewer 1: Q11
\begin{review}
As for the other lighting and imaging protocols adopted by the authors (Sec. $3.2.1$ and $3.2.2$), do they interfere with plant growth?
\end{review}

\begin{response}
\todo{Jin}
\end{response}

% Reviewer 1: Q12
\begin{review}
At the end of the first paragraph of Sec. $4.4$, p. $8$, the authors envision a use of the multiple modalities in their dataset in which algorithms are developed to handle missing modalities.
Briefly presenting a use case scenario or citing relevant works may help clarify the importance of this point.
\end{review}

\begin{response}
In this use case scenario, the training part of leaf segmentation algorithms may have both the RGB and depth modalities, while during the testing, we may only have the RGB modality available.
This scenario is useful because it leverages additional information during the training, while does not increase the hardware/sensor cost during the testing.
Specifically, we may use two types of approaches to implement this scenario.
One is called learning with side information, which is the depth modality in this example (see~\cite{chen2013boosting}).
The other is to use transfer learning that handles missing modality in the target domain (see~\cite{ding2014latent}).
\end{response}

@@

% Reviewer 1: Q15
\begin{review}
The acronym "MSU-PID" should be clearly defined when it first appears in text (p. $2$, line $51$)
\end{review}

\begin{response}
Except in the Abstract, the "MSU-PID" first appears in paragraph $4$ of Sec. $1$.
We have clearly defined it as short for Michigan State University Plant Image Database.
\end{response}

% Reviewer 1: Q16
\begin{review}
According to the SI (International System of Units), units of measure should be written in roman type, while italic type is reserved for variables.
Besides, when they follow a number, a space should be included between numerical value and unit symbol.
To improve clarity of the manuscript, the authors are therefore advised to adhere to the SI style conventions.
\end{review}

\begin{response}
We have changed the inaccurate annotations to adhere to the SI style conventions. 
\end{response}

@@

\vspace{1em}
\noindent {\large\textsc{Reviewer~2}}\\
\begin{tabular*}{\textwidth}{c}
\hline
\end{tabular*}

% Reviewer 2: Q21
\begin{review}
The authors argue that the most closely related work is that of Scharr et al $2014$.
They identify as weaknesses that it i) uses only RGB images and ii) can be used for a few vision problems.
However, upon reading the Scharr paper it is clear that the authors of that work, do mention that they collect additional data to be used in tracking context and for other applications.
It is not clear if the authors here refer to what is available data from Scharr et al or what is described in the paper?
Furthermore, the data in Scharr et al appear to originate from different mutants and under different treatments, and also imaged with different cameras.
Since this work does use only wildtypes and single cultivars this distinction should be made.
Furthermore, once leaf labeling is available several secondary annotations can be derived so in some sense Table $1$ should be annotated accordingly.
Nevertheless, I recommend the authors for arranging information as in Table $1$.
\end{review}

\begin{response}
We refer to Scharr et al $2014$ that the Leaf Segmentation Challenge database only includes independent images without tracking context.
Please refer to Comment $9$ for the reason we do not include mutants.
\todo{Are we going to have mutants in bean data?}
% is that we assume any computer vision algorithms that work on wildtypes should also work well on mutants as they have similar structure.
\\ %\textcolor{red}{I do not understand what to be added to Table $1$.}
% \todo{TBD: Dr. Chen, please add some sentences about mutants in bean data. I recall we plan to capture additional bean data sets that have different mutants. Am I right?}
\end{response}

% Reviewer 2: Q22
\begin{review}
The authors do a nice work of calibrating the cameras and measuring noise in the depth camera.
However, in page $2$ introduction says that this calibration allows for the explicit correspondence between pixels of any modality.
The authors rely on this to annotate data in one modality and propagate labels in the other (at least this is what I understand from later on description of methodology).
However, this is a VERY strong assumption and depends completely on the distance between the cameras, the angles, the distance between object and sensors and the actual object arrangement.
From our experience even when imaging co-planar plants (such as young Arabidopsis) at a distance of $\sim 70$ cm even when the camera sensors are really close to each other (less than $5$ cm) some differences in view are there and occlusions are present.
The authors should comment on this and should show as supportive evidence examples of plants at different growth stages in all $4$ modalities in raw and annotated form to show how close this correspondence is matching and how the propagated labels.
Furthermore, additional supporting evidence could be obtained either by arranging for two external and blind annotators to label some data (different age, different placement in the tray to show the effect of angle) in another modality (e.g., optical) and then measure inter-observer variability.
Then they can propagate annotations from fluorescence to images of that modality and measure agreement.
If this agreement is better than the in between rater variability then you could argue that propagating annotations is ok to do and actually beneficial.
Nevertheless, you should definitely mention this limitation of your work.
\end{review}

\begin{response}
We expanded our description of the labeling and the propagation to other modalities in the paper.  
The data labeling is performed in the fluorescence image modality.  
The infra-red image is from the same camera and so pixel labeling will be identical.  
The labels are propagated to the color and depth modalities using planar homographies.  
The homography between the fluorescence image and the color image is calculated by fitting matching features in these modalities, and the homography to the depth image is found by fitting a plane through the $3$D plant points.  
As the reviewer noted, using these homographies will result in pixel segmentation errors due to parallax for plant regions outside of the modeled planes.  
We evaluate these errors qualitatively and quantitatively.  
Figure $6$ illustrates the label propagations from the fluorescence image to the other modalities and from the color image to other modalities with two different line colors.  
Errors occur where the lines fail to overlap and are due to propagation effects as well as boundary selection variations by the labeler between modalities.  
We compare the magnitude of these two effects in Table $4$. 
The performance of label propagation is only slightly worse than the performance of another annotator. 
Therefore, we propagate the fluorescence labels to other modalities for Arabidopsis plants. 
As for bean plant, the homograph-based mapping performed poorly due to the large within-plant depth variations. 
So we only provide the labels for bean plant in fluorescence and IR as they use the same camera. 
Please refer to Sec. $4.3$ for more details. 
\end{response}

@@

% Reviewer 2: Q25
\begin{review}
On Table $3$ you list resolutions for the acquired image data.
This image resolution is much lower than the LSC database of Scharr et al.
This limitation should be mentioned.
\end{review}

\begin{response}
We added one paragraph in the end of Sec. $4.1$ to address the trade-off between image resolution and experiment throughput.
\end{response}

% Reviewer 2: Q26
\begin{review}
On manual annotation process, did you use an extra annotator or a supervisor?
\end{review}

\begin{response}
The released label is labeled by one annotator.
However, we do use an extra annotator to label several images and the annotation error between different annotators is evaluated.
As shown in Table $4$, the average annotation similarity in case of {\it{SBD}} score is around $0.847$ for fluorescence and $0.858$ for RGB images. 
Different annotators have more agreement on the labeling as the plant grows. 
This is due to the evaluation metric {\it{SBD}}, which favors bigger leaves. 
\end{response}

@@

% Reviewer 2: Q31
\begin{review}
Based on your annotations can you find which leaf occludes which?
\end{review}

\begin{response}
During annotation, we can observe which leaf occludes which and annotate the overlapping area to the leaf on top.
However, it is hard to estimate which leaf occludes which from the annotations.
\end{response}

% Reviewer 2: Q32
\begin{review}
The authors test an algorithm (developed by them) on the fluorescence part of the data.
Granted this algorithm is presented elsewhere on the same data.
I was wondering if the authors can either a) use the same algorithm on one of the other modalities, and how it would perform (assuming ground truth labeling obtained via propagation)?
OR b) if they can apply another benchmark method even from the broad CV literature on one of the CV problems considered in another modality.
I think doing one of the two, time permitting, will greatly assist the paper.
\end{review}

\begin{response}
We have applied our algorithm on the RGB images while the groudtruth label is generated via label propagation. 
The performance on RGB images is shown in Figure $9$ and $10$.  
\end{response}

### 2015-07-26 datapaper.tex
baseline-performance-on-rgb-images
edit-on-response-letter

Among many applications of machine vision, plant image analysis has recently began to gain attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants and improving crop yield.
Despite its importance, the lack of publicly available research databases containing plant imagery has substantially hindered the advancement of plant image analysis.
To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
First, MSU-PID is captured using four types of imaging sensors, fluorescence, infrared (IR), RGB color, and depth.
Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.
%
%Among many applications of machine vision, plant image analysis has recently begin to gain attentions due to its potential huge impact to plant visual phenotyping, the understanding of plant growth, the quality of crops, and the improvement of the yield.
%Despite its importance, the pack of publicly available research database of plant imagery has substantially hindered the advancement of plant image analysis.
%To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
%First, MSU-PID is captured using four types of imaging sensors, Fluorescence, infrared (IR), RGB color, and depth.
%Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
%We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.

@@

%\input{calibtable.tex}

>>>>

Among many applications of machine vision, plant image analysis has recently began to gain attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants, and improving crop yield.
Despite its importance, the lack of publicly available research databases containing plant imagery has substantially hindered the advancement of plant image analysis.
To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
First, MSU-PID is captured using four types of imaging sensors, fluorescence, infrared (IR), RGB color, and depth.
Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.
%
%Among many applications of machine vision, plant image analysis has recently begin to gain attentions due to its potential huge impact to plant visual phenotyping, the understanding of plant growth, the quality of crops, and the improvement of the yield.
%Despite its importance, the pack of publicly available research database of plant imagery has substantially hindered the advancement of plant image analysis.
%To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
%First, MSU-PID is captured using four types of imaging sensors, Fluorescence, infrared (IR), RGB color, and depth.
%Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
%We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.

@@
